Project 1

### 2018-09-10 Project1/report/ms.tex
Updates from ShareLaTeX

\subsection{Program CPU time}
\begin{deluxetable}{lccc}
%\tablewidth{0pt}
\tablecaption{\label{tab:results}}
\tablecomments{This table contains average CPU times for all the algorithms}
\tablecolumns{4}
\tablehead{Column 1  & Column 2 & Column 3 & Column 4}
\startdata
Item 1 & Item 2 & Item 3 & Item 4
\enddata
\end{deluxetable}

>>>>

\subsection{Program CPU time}
\begin{deluxetable}{lccc}
%\tablewidth{0pt}
\tablecaption{\label{tab:results}}
\tablecomments{This table contains highest, lowest and average measured CPU times for the different algorithms used at n = 10^{6}}
\tablecolumns{4}
\tablehead{ & General & Taylored & Armadillo}
\startdata
Highest & Item 2 & Item 3 & Item 4 \\
Lowest & Item 2 & Item 3 & Item 4 \\
Average & Item 2 & Item 3 & Item 4 
\enddata
\end{deluxetable}
